Nitric-oxide-feedback to ciliary photoreceptor cells orchestrates UV avoidance in zooplankton

### 2022-05-20 text/Manuscript.Rmd
Figure4 add
Figure5 add

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

NIT-GC1 has a highly conserved cyclase domain and activation of NIT-GC1 is expected to produce cGMP. Recently, a synthetic protein called Green cGull was developed as a cGMP indicator that can be used in cultured cell systems (Matsuda et al., 2017). We co-expressed Green cGull and NIT-GC1 in cultured cells COS-7 (monkey kidney) and tested the intracellular dynamics of cGMP in the activation of NIT-GC1. First, S-nitroso-N-acetyl-DL-penicillamine (SNAP; NO donor), 8-Br-cGMP (8-Bromoguanosine 3',5'-cyclic monophosphate; membrane-permeable cGMP analogue, positive control) and DMSO (negative control) were applied to COS-7 cells expressing Green cGull only. 8-Br-cGMP increased fluorescence intensity by more than sixfold, while little changes were detected for SNAP and DMSO (Fig. 4A). Nest, the two kind of genes, Green cGull and NIT-GC1, were co-expressed using the 2A self-cleaving peptide and the same solutions were applied. As a result, a clear increase in cGMP fluorescence intensity was detected in SNAP compared to DMSO or expression of Green cGull only, although not as high as the increase in 8-Br-cGMP (Fig. 4B). Finally, expression of a mutant form of NIT-GC1 with deletion of the NIT domain significantly suppressed the increase in cGMP (Note, we need re-experiment!, Fig. 4C). These results indicate that NIT-GC1 is activated by NO to produce cGMP. They also show that the NIT domain is required for the activation of NIT-GC1.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

@@

NIT-GC1 has a highly conserved cyclase domain and activation of NIT-GC1 is expected to produce cGMP. Recently, a synthetic protein called Green cGull was developed as a cGMP indicator that can be used in cultured cell systems (Matsuda et al., 2017). We co-expressed Green cGull and NIT-GC1 in cultured cells COS-7 (monkey kidney) and tested the intracellular dynamics of cGMP in the activation of NIT-GC1 (Fig. 4A). First, S-nitroso-N-acetyl-DL-penicillamine (SNAP; NO donor), 8-Br-cGMP (8-Bromoguanosine 3',5'-cyclic monophosphate; membrane-permeable cGMP analogue, positive control) and DMSO (negative control) were applied to COS-7 cells expressing Green cGull only. 8-Br-cGMP increased fluorescence intensity by more than sixfold, while little changes were detected for SNAP and DMSO (Fig. S4A). Next, the two kind of genes, Green cGull and NIT-GC1, were co-expressed using the 2A self-cleaving peptide and the same solutions were applied. As a result, a clear increase in cGMP fluorescence intensity was detected in SNAP compared to DMSO or expression of Green cGull only, although not as high as the increase in 8-Br-cGMP (Fig. 4B, C). Finally, expression of a mutant form of NIT-GC1 with deletion of the NIT domain significantly suppressed the increase in cGMP (Note, we need re-experiment!, Fig. 4D). These results indicate that NIT-GC1 is activated by NO to produce cGMP. They also show that the NIT domain is required for the activation of NIT-GC1.

![Figure 4. Legend goes here](../figures/Figure4.png){width="100%"}
